---
title: "Lab 11 - Logistic Regression"
subtitle: "STAT 242: Intermediate Statistics"
output: pdf_document
---

```{r setup, echo=FALSE}
## Load libraries
library(MASS)

## Load data
MedGPA <- read.csv("https://marievozanne.github.io/stat340_f2020/data/MedGPA.csv")
```


## Medical School Admissions.

#### The data for Medical School Admissions is in MedGPA.csv, taken from undergraduates from a small liberal arts school over several years. We are interested in student attributes that are associated with higher acceptance rates.

- `Accept` = accepted (A) into medical school or denied (D)
- `Acceptance` = accepted (1) into medical school or denied (0)
- `Sex` = male (M) or female (F)
- `BCPM` = GPA in natural sciencces and mathematics
- `GPA` = overall GPA
- `VR` = verbal reasoning subscale score of the MCAT
- `PS` = physical sciences subscale score of the MCAT
- `WS` = writing samples subscale score of the MCAT
- `BS` = biological sciences subscale score of the MCAT
- `MCAT` = MCAT total score
- `Apps` = number of schools applied to

For this lab, we will use `Acceptance`, `GPA`, and `MCAT`.

#### (a) Fit a logistic regression model with `Acceptance` as the response variable, and `GPA` as the explanatory variable. Since we have not discussed the assumptions for logistic regression in detail yet, you may assume that the assumptions are met.

```{r}

```


#### (b) Interpret the effect of `GPA` on the log odds of acceptance into medical school.




#### (c) Interpret the effect of `GPA` on the odds of acceptance into medical school.



#### (d) Examine the p-value associated with `GPA` in the model summary. What hypothesis do you think this corresponds to? What are the conclusions of this hypothesis test, based on your p-value?



#### (e) Fit a logistic regression model with `Acceptance` as the response variable, and `MCAT` as the explanatory variable. Since we have not discussed the assumptions for logistic regression in detail yet, you may assume that the assumptions are met. 

```{r}

```


#### (f) Interpret the effect of `MCAT` on the log odds of acceptance into medical school.



#### (g) Interpret the effect of `MCAT` on the odds of acceptance into medical school.



#### (h) Examine the p-value associated with `GPA` in the model summary. What hypothesis do you think this corresponds to? What are the conclusions of this hypothesis test, based on your p-value?



#### (i) Is there any evidence that the effect of MCAT score or GPA differs for males and females (hint: think different slopes)? Use what you know from linear regression to fit two models to address this question, one with `MCAT` and `Sex` in it, and the other with `GPA` and `Sex` in it, and to conduct the appropriate hypothesis tests.

```{r}

```



- Note, we will discuss more models like the one in (i) formally on Thursday -- this last exercise is intended to give you an introduction into some of what we will be thinking about in class.

## References

A. Cannon et al. 2018. Package Stat2Data. "https://cran.r-project.org/web/packages/Stat2Data/Stat2Data.pdf"

P. Roback and J. Legler. 2020. \emph{Beyond Multiple Linear Regression: Applied Generalized Linear Models and Multilevel Models in R}.

